---
title: "ANOVA"
geometry: margin = 2.5cm
header-includes:
- \usepackage[T1]{fontenc}
- \usepackage{lmodern}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead{}
- \lhead{Report 1}
- \rhead{Vos, Ben Mahmoud, Schmidt}
- \headheight = 15pt
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
  html_document:
    df_print: paged
pagenumbering: yes
fontsize: 12pt
toc: no
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

In the article \cite{article}, some rotten apples are studied. We analyse their data.

# Data exploration

```{r load apple data}
apple<-read.table("./apple.txt",col.names = c("varieties","strains","days","weight","radius","advance","rate"))
apple$varieties<-as.factor(apple$varieties)
apple$strains<-as.factor(apple$strains)

#mean_rate_var<-tapply(apple$rate, list(apple$varieties), mean)
#tapply(apple$rate, list(apple$strains), mean)
#tapply(apple$rate, list(apple$varieties), sd)
#tapply(apple$rate, list(apple$strains), sd)
#tapply(apple$advance, list(apple$varieties, apple$strains), mean)
#tapply(apple$advance, list(apple$varieties, apple$strains, apple$days,apple$weight,apple$radius), mean)
```

```{r plot}
layout(matrix(1:2,ncol=2))
boxplot(advance~apple$varieties,data=apple,xlab="Apple Variety",ylab="Fungal Radial Advance [cm]")
boxplot(rate~apple$varieties,data=apple,xlab="Apple Variety",ylab="Advance Rate [cm/day]")

layout(matrix(1:2,ncol=2))
boxplot(advance~apple$strains,data=apple,xlab="Fusarium Strain",ylab="Fungal Radial Advance [cm]")
boxplot(rate~apple$strains,data=apple,xlab="Fusarium Strain",ylab="Advance Rate [cm/day]")
```




```{r brute force du modèle}

apple.aov<-aov(rate~varieties+strains, data=apple)
summary(apple.aov)
coef(apple.aov)

#layout(matrix(1:4,ncol=2))
#plot(apple.aov) -> ça marche pas pour le pdf


```

# Next part
Allow to see that wonderful header

\begin{thebibliography}{9}
\nocite{article}


\bibitem{article}

A. S. Horne Frederick Gugenheim Gregory Vernon Herbert Blackman {"A quantitative study of the course of fungal invasion of the apple fruit, and its bearing on the nature of disease resistance.—Part II. The application of the statistical method to certain specific problems"}. \textbf{102}. \textit{Proceedings of the Royal Society of London. Series B, Containing Papers of a Biological Character}
http://doi.org/10.1098/rspb.1928.0018
\end{thebibliography}

